\textbf{SPECFEM3D}\\ \textbf{Cartesian}\\ \textbf{User Manual}

### 2021-10-13 doc/USER_MANUAL/05_running_the_solver.tex
updates doc about STF

\item The zero time of the simulation corresponds to the center of the triangle/Gaussian,
or the centroid time of the earthquake. The start time of the simulation
is $t=-1.5*\texttt{half duration}$ (the 1.5 is to make sure the moment
rate function is very close to zero when starting the simulation).
To convert to absolute time $t_{\mathrm{abs}}$, set
%
\begin{lyxcode}
$t_{\mathrm{abs}}=t_{\mathrm{pde}}+\texttt{time shift}+t_{\mathrm{synthetic}}$
\end{lyxcode}

>>>>

\item The zero time of the simulation corresponds to the center of the triangle/Gaussian,
or the centroid time of the earthquake. The start time of the simulation
is $t=-2.0*\texttt{half duration}$ (the 2.0 factor is to make sure the moment
rate function is very close to zero when starting the simulation. This avoids spurious high-frequency oscillations.
Also, for acoustic simulations using a Gaussian STF this is set to a factor 3.0, while Ricker source time functions use a factor 1.2).
To convert to absolute time $t_{\mathrm{abs}}$, set
%
\begin{lyxcode}
$t_{\mathrm{abs}}=t_{\mathrm{pde}}+\texttt{time shift}+t_{\mathrm{synthetic}}$
\end{lyxcode}
